EpiExpert Crowd-Forecasting Performance Board

### 2021-03-11 evaluation/report-template.Rmd
update report template

This is our evaluation of forecasting models and individual forecasters who have contributed forecasts of Covid-19 case and death numbers in Germany and Poland. These forecasts were submitted to the 
[German and Polish Forecast Hub](https://github.com/KITmetricslab/covid19-forecast-hub-de)
each week.

The evaluations are our own and not authorised by the German Forecast Hub team. We cannot rule out mistakes 
and the analyses are subject to change.

@@

>>>>

This is our evaluation of forecasting models and individual forecasters who have contributed forecasts of Covid-19 case and death numbers in Germany and Poland. These forecasts were submitted to the 
[German and Polish Forecast Hub](https://github.com/KITmetricslab/covid19-forecast-hub-de)
each week. Currently, we submit an unweighted mean ensemble to the Forecast Hub, but this will likely be changed in the future. We will transition to submitting forecasts to the [European Forecast Hub](https://github.com/epiforecasts/covid19-forecast-hub-europe) in the future. 
The evaluations are our own and not authorised by the German Forecast Hub team. We cannot rule out mistakes 
and the analyses are subject to change.

@@

You can register to become a forecaster [here](https://cmmid-lshtm.shinyapps.io/crowd-forecast/).
